\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Software Engineer}
    {Under Armour}
    {San Francisco, U.S.A}
    {Jan. 2016 - May 2018}
    {
      \begin{cvitems}
	\item{Developed and maintained a payment system to manage paid subscriptions for MyFitnessPal and MapMyFitness that resulted in simplified accounting, improved revenue metrics, while reducing costs. This system handled millions of dollars per month in transactions. }
	\item {Designed and implemented a feed service used in all Under Armour's apps, that reduced the cost of storage while improving the response time.}
        \item {Designed a service to manage user friendships and help develop social interactions within the apps using a graph database from Amazon Neptune. }	
	\item {Mentored a Junior Engineer by assigning tasks and helping them get up to speed with the organization methods and tools.}
      \end{cvitems}
    }
    
  \cventry
    {Software Engineer}
    {MyFitnessPal}
    {San Francisco, U.S.A}
    {Sept. 2014 - Jan. 2016}
    {
      \begin{cvitems}	
        \item{Improved scalability and response times of core backend services by improving data storage, reducing response time and lowering error rates. The overall success of our app lead to the acquisition of MyFitnessPal by Under Armour for \$475 million.}
        \item {Lead the successful migration of all the organization's services to a new email provider, without interruption, while sending millions of emails every month. Developed a service that managed email templates and contents, and pushed notifications to improve marketing conversion rates.}
        \item {Developed libraries to help teammates work faster and be more productive through cross-team tool uniformity. The tool helped engineers debug and reduce maintenance time.}
        \item{Developed internal tools to manage paid features and subscriptions, giving more visibility and control to the Customer Happiness team. It reduced the time required to assist paid users, and increased paid conversion.}
      \end{cvitems}
    }


  \cventry
    {Software Engineer}
    {Rewarder}
    {San Francisco, U.S.A}
    {Nov. 2011 - Sep. 2014}
    {
      \begin{cvitems}
        \item {Developed a Stripe integration for securely accepting customers credit card payments, and built a balance management and cash out system to keep track of the transactions.}
        \item {Maintained a Rails application and developed an API to enable the development of a mobile app.}
        \item {Built a partner integration system used by Ask.com and ManualsOnline.com, resulting in an increase in traffic.}
        \item {Built an API integration with Ebay to power a new "Wanted" feature on the Ebay website. Worked closely with an Ebay engineer on the technical design and integration.}
        \item{Built a text messaging communication system for notifications and events with Twilio API.}
      \end{cvitems}
    }
    
  \cventry
    {Intern Software Engineer}
    {Taskrabbit}
    {San Francisco, U.S.A}
    {Apr. 2011 - Oct. 2011}
    {
      \begin{cvitems}
        \item {Developed a Facebook Application for friend referrals.}
        \item{Completed integration testing for feature implementation, regression testing, and site stability.}
        \item{Built a messaging feature for task clarification.}
      \end{cvitems}
    }
\end{cventries}
